A Switching Planner for Combined Task and Observation Planning

### 2011-02-07 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
shrinking related work section

More generally, there has been much recent work on scaling POMDP
solution procedures to medium-sized
instances~\cite{shani:etal:08,KurHsu08}. In that
setting \citeauthor{kurniawati:etal:2010}~(\citeyear{kurniawati:etal:2010})
recently addressed an inefficiency of offline point-based techniques
in problems with medium length planning horizons, however their
approach take tens of minutes to good plans, and only scales to tens
of thousands of states. In the case of general domain-independent
factored systems, the state-of-the-art scales to relatively small
problems with $2^{22}$ states~\cite{shani:etal:2008}. At their limit,
these procedures take over an hour to converge, and $\sim10$ seconds
on average to perform a single Bellman backup.  For classes of POMDP
that feature exploitable structures (e.g., no actions with negative
effects), problems with as many as $10^{30}$ states can be targeted by
such offline procedures~\cite{brunskill:russell:2010}. Moving someway
towards addressing real-time decision making, recent online POMDP
solution procedures have been developed which can exploit highly
approximate value functions -- typically computed using a point-based
procedure -- and heuristics in forward
search~\cite{ross:etal:2008}. Their applicability in our setting is
limited, firstly because they only scale to smaller problems, with
thousands of states, and also due to the large amount of
\emph{problem-specific} offline processing that might be required to get useful
search guidance. A {\em very} recent and promising online approach for
large POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.

>>>>

There has also been much recent work on scaling offline approximate
POMDP solution procedures to medium-sized instances. Recent
contributions propose more efficient belief-point sampling
schemes~\cite{kurniawati:etal:2010,shani:etal:08}, and structured
representations with procedures that can efficiently exploit
them~\cite{brunskill:russell:2010,shani:etal:2008}. Offline domain
independent systems scale to {\em logistics} problems with $2^{22}$
states~\cite{shani:etal:2008}, taking over an hour to converge, and
around 10 seconds on average to perform each Bellman
backup. \citeauthor{brunskill:russell:2010} are able to solve problems
with as many as $10^{30}$ states, by further exploiting certain
problem features -- E.g., no actions with negative effects.
%%
Moving someway towards supporting real-time decision making, recent
online POMDP solution procedures have been developed which leverage
highly approximate value functions -- computed using an offline
procedure -- and heuristics in forward
search~\cite{ross:etal:2008}. These approaches are applicable in
relatively small problems, and can require
expensive \emph{problem-specific} offline processing in order to yield
good behaviours.
%%
A {\em very} recent and promising online approach for
large POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.

%% Their applicability in our setting is
%% limited, firstly because they only scale to smaller problems, with
%% thousands of states, and also due to the large amount of
%% \emph{problem-specific} offline processing that might be required to get useful
%% search guidance.

%%  In that
%% setting \citeauthor{kurniawati:etal:2010}~(\citeyear{})
%% recently addressed an inefficiency of offline point-based techniques
%% in problems with medium length planning horizons, however their
%% approach take tens of minutes to good plans, and only scales to tens
%% of thousands of states. In the case of general domain-independent
%% factored systems, the state-of-the-art scales to relatively small
%% problems with $2^{22}$ states~\cite{shani:etal:2008}.

%% At their limit,
%% these procedures take over an hour to converge, and $\sim10$ seconds
%% on average to perform a single Bellman backup.  For classes of POMDP
%% that feature exploitable structures (e.g., no actions with negative
%% effects), problems with as many as $10^{30}$ states can be targeted by
%% such offline procedures~\cite{brunskill:russell:2010}.
